How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-05 tse-paper/content.tex
mark where we answer RQs 2.x

\subsection{Results}
% tense: past
\addtolength{\tabcolsep}{-5pt}
\label{sec:litsurresults}

@@

\subsubsection{Which analysis techniques exist? (RQ 1.2)}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

@@

\emph{Running a
chunk retrieval technique} means
% TODO what does it mean ``to apply?''
applying a fully configured
technique to a build log.
The technique then outputs a (possibly empty) list of substrings of the
build log text.

@@

% TODO Caro, can you check this? Also I did not find any literature
% references to CTS.
It does not seem to be a common technique?
% Where does the name come from then?
Finally, from the fields of information retrieval (IR) and natural
language
processing (NLP), we leverage a
\emph{Common Text Similarity (CTS)} approach.
The inspiration behind it---apart from literature indicating the use
of IR and NLP (\Cref{tab:litsur:techniques})--- is that the relevant,
failing parts of build logs often looks similar to each other, even if
the exact failure reason might differ.

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
%% TODO Caro: I took this out as it interrupts reading flow.
%% Do you
%% agree?
%% Indeed, this was one of the
%% most common approaches we took when searching for the reason a build
%% failed while creating the \emph{LogChunks} data
%% set~\cite{brandt2020logchunks}.
To investigate the performance of this approach, we designed a chunk
retrieval technique mimcing this human behavior based on keyword
search.

\subsubsection{Configuration}
A set of keywords configures the chunk retrieval with KWS\@.
To better
compare KWS with PBE and CTS, we also configure it through examples.
% TODO (resolved) associate is very abstract and tells us
% less about what is going on than the new version
From each example, we extract a list of keywords that we hope should
also appear in, or close to, the targeted chunk of new input.
Finally, we merge the lists from all examples to build one unified
list of the most commonly occurring keywords for the search with KWS.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
To fully comprehend how difficult the task of build log analysis really
is without any a priori knowledge, we include a comparison with a
baseline of
picking lines at random from the build log.
RLR mimics the
situation of guessing blindly which lines are interesting.
The only configuration option for RLR is the number of lines it should
retrieve.
For a comparison to the other techniques (whose number of
% TODO Caro: but wait, this is not really true for KWS, right?
returned lines is dynamic), we configure RLR to return the average
number of lines in the chunks of the training examples.

@@

% TODO Caro: I like this explanation of structural categories and
% would leave it here (slightly adapted), but I think
% struct.
categ.
should be mentioned earlier -- not sure if you know a
% better place, but how about sec.
3.1? i don't think people should
% have to read an example section -- which they might skip -- to
% get to know of this important concept!

@@

CTS will rank the lines from an analyzed build log which are most
similar to the chunks in the training examples
from \Cref{lst:chunk-example}.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
% TODO Caro: How well does it deal with the third example?

@@

% TODO: decide if keep or redo
% if keep, Caro do noted improvements
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
  clip]{img/study.pdf}
	\caption{Study design of the technique comparison study.}
	\label{fig:study}
\end{figure*}

In the literature survey, we noted that previous work seemed to choose
a log analysis technique arbitrarly and that is a lack of guidance on
when to use which technique.
% add (see \Cref{sec:lit-sur:discussion}) ?
To address this, in this section, we conduct an empirical study
comparing the three novel chunk retrieval techniques we presented in
\Cref{sec:techniques}.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} How do build log analysis techniques compare?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] With how many examples does a technique
  perform best?
  \item[\textbf{RQ2.2:}] How structurally variable can configuration
  examples be?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

For each build log in \emph{LogChunks}, we manually marked
the chunk that describes why the build
failed---the information targeted by most of the works in our
literature survey (see \Cref{sec:lit-sur:discussion}).
To be able to configure the keyword search technique,
% TODO (resolved) the data set cannot associate anything
we associated each chunk in the data set with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
% TODO Are surrounding markings really the only structural
% category element? I doubt that
If the chunks were, for example, surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

% TODO what does this refer to here? Make it clearer.
%It would refer to the strcutrual categories but
% that is already in the list?

% TODO couldn't it also be chunks? why corresponding?
As explained in \Cref{sec:crt-characteristics}, examples are the basic
unit by which we configure each technique.
The full build log text,
chunk(s), search keywords, and the assigned structural categories make
up one \emph{example} in \emph{LogChunks}.

@@

% TODO Didn't we above define ``run'' instead of apply?
% Shouldn't we then also use it here?
% TODO wow, this starts already super confusing
We run each of the three chunk retrieval techniques
on all of the 80 projects in
\emph{LogChunks} \circlenum{1}.
For each project, we select training sets of size 1, 2, \dots 5
\circlenum{2}.
We vary the training set size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).

@@

\resizebox{\columnwidth}{!}{%
\centering
\begin{tabular}{llll}
  \toprule
  & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\
  \midrule
  \textbf{Structural Categories} & 1 & less is better & \makecell[l]{best
  1 \\
  multiple okay} \\
  \midrule
  \textbf{Training Set Size} & 2 & no influence & 2 \\
    \midrule
  \textbf{Precision} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  low \\
    \midrule
  \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium &
  high \\
    \midrule
  \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
  & high & low &
  \makecell[l]{low (precision) \\ high (recall)} \\	\midrule
  \textbf{Output Consumer} & program & human & human \\
  \bottomrule
\end{tabular}%
}
\end{table}

@@

\noindent
\textbf{Configuration and Input.}
The study results show that chunk retrieval with PBE gives best
results when the log chunks are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based
programs~\cite{mayer2015user}.
PBE is thus suited to retrieve information
chunks that always have the same defining surrounding or internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to start and
end the same way.

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
In fact, unless they
were in some sense redundant, adding more training examples even
hindered the applicability of PBE.

\noindent
\textbf{Retrieval Output Usage.}
If the program synthesis succeeds and applying the regular expression
program yields an output, PBE has high precision and recall.
The technique
clearly identifies a failing synthesis or when the regular expression
finds no match on a build log.
Therefore, if PBE produces
an output, the user can have high confidence that it is the desired
output.
This preciseness makes output from PBE chunk retrieval
well-suited for machine consumption and therefore automatic onward
processing.

\subsubsection{Common Text Similarity (CTS)}
\noindent
\textbf{Configuration and Input.}
Similar to PBE, chunk retrieval using CTS yields better results the
fewer structural categories are present in the training and test
examples.

The number of training examples had no noticeable influence on
precision or recall.
Information retrieval techniques
like text similarity commonly learn on a higher number of examples
than we chose in the study.
Future work should investigate how many
examples yield improvements in the chunk retrieval over a single
training example.

\noindent
\textbf{Retrieval Output Usage.}
CTS has good precision and recall on average, though with a high
variation.
This means that the quality of an output by CTS is hard to
determine, which makes it unsuited for automatic processing and requires
a human to further inspect and interpret the output.
This could include semi-automated procedures such as sending
developers an email with the extracted build failure reason.

\subsubsection{Keyword Search (KWS)}
\noindent
\textbf{Configuration and Input.}
KWS has a higher recall than the two other techniques for multiple
structural categories present in the training and test examples.
This
makes KWS a good technique if there is little prior knowledge of how
the targeted log chunk is represented in the build log.
For the
example of extracting the reason the build failed, KWS is best suited
if a build can fail in various steps logged by different build
tools and no
pre-categorization of where the build failed is available.

Going from one to two training examples, KWS's recall improves
significantly.
However, further enlarging the training set
does not lead to further improvements.

\noindent
\textbf{Retrieval Output Usage.}
While KWS has the highest recall of all three techniques, its
precision is the lowest.
The output of a chunk retrieval with KWS is
well-suited to be read by humans, but ill-suited for consumption by
automated tools.

@@

The first and most important aspect that influences the decision for a
chunk retrieval technique is the presence of different structural
categories in the log (or lack therefore).
Are the targeted log
chunks always present in the same structural way within the build logs
(first question in \Cref{fig:crt-recommendation})?  If so, the chunks
in all training examples and the analyzed build log are in the same
structural category
%TODO ...
and what? PBE is the best technique?
If the chunks are from multiple structural categories and recall is
more important than precision, we recommend to use KWS\@.
% TODO because ?

@@

% TODO Caro: fill in the maven analyzer plugin and others.
\textbf{Limitation to Scholarly Articles.} We limited our literature
survey to scholarly articles.
However, the field of build log analysis is extremely relevant to
practitioners, too.
While it is difficult to systematically sight all such non-scientific
material, we ran several Google search queries related to build log
analysis and evaluted them informally.
Our findings include the Jenkins build log analyzer and a web page
on which Microsoft details how its CI service, Azure Pipes, uses a
PBE-approach for certain log formats such as Python.
This inspired the choice of PBE in \Cref{sec:choice}.

@@

% TODO (resolved)
% kinda uncreative..
% not sure what another example would be?
% not sure if this adds much on top of the sentences further up
%% Yup, it's super cool and I expanded it a bit
Overall, we believe our implementations and their weaknesses stand
prototypical for the techniques.
We tried to limit idiosyncrasies as
much as possible, by choosing standard approaches and minimizing
configuration, instead of parameterizing and fine-tuning methods
specific to our data set.

@@

\textbf{Few Samples with Many Structural Categories.}
Our comparison study includes fewer measurements with many structural
categories than with one structural category category (50.25\% one,
% TODO This does not add up to 1.
Please no decimals,
% we do not need so much precision here.
Also tell % of what?
33.75\% two, 13.75\% more than two).
This distribution mirrors the
structural categories in a real-world data set, where there were
mostly few structural categories within one project.
In addition, the
third of the measurements we conducted with two structural categories
already showed the negative effect of an increasing number of
structural categories on the performance of the chunk retrieval
techniques.

\section{Future Work}
In this section, we describe what we believe are fruitful future
research directions in the field of build log analysis.
We base our
assessment on the results of the literature survey and combine it with
findings from our technique comparsion study.

@@

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
% TODO Passive overflow
The keywords, for example, can be
investigated to answer which keywords are used to search for the
reason the build failed within build logs.

@@

We evaluated the performance of these chunk retrieval techniques on the
\emph{LogChunks} data set and saw varying results.
CTS had the highest average F$_{1}$-score with 51\%, while the other
techniques showed higher average scores for precision (95\%, PBE) and
recall (70\%, KWS).
Overall, all technqiues vastly outperformed a
baseline of random line retrieval.

>>>>

\subsection{Results}
% tense: past

\label{sec:litsurresults}

@@

\subsubsection{Which analysis techniques exist? (RQ 1.2)}

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

@@

\emph{Running a
chunk retrieval technique} means
% TODO what does it mean ``to apply?''
% C: run vs apply / show 332 heading / maybe take only run
applying a fully configured
technique to a build log.
The technique then outputs a (possibly empty) list of substrings of the
build log text.

@@

% TODO Caro, can you check this? Also I did not find any literature
% references to CTS.
% It does not seem to be a common technique?
% Where does the name come from then?

% C: text similarity and three letter acronyms
Finally, from the fields of information retrieval (IR) and natural
language
processing (NLP), we leverage a
\emph{Common Text Similarity (CTS)} approach.
The inspiration behind it---apart from literature indicating the use
of IR and NLP (\Cref{tab:litsur:techniques})--- is that the relevant,
failing parts of build logs often looks similar to each other, even if
the exact failure reason might differ.

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
%% TODO Caro: I took this out as it interrupts reading flow.
%% Do you
%% agree?
%% Indeed, this was one of the
%% most common approaches we took when searching for the reason a build
%% failed while creating the \emph{LogChunks} data
%% set~\cite{brandt2020logchunks}.

% C: motivation for KWS in LogChunks Paper
% yeah we can maybe leave that out here (move to 'choice for crt'?)

To investigate the performance of this approach, we designed a chunk
retrieval technique mimicking this human behavior based on keyword
search.

\subsubsection{Configuration}
A set of keywords configures the chunk retrieval with KWS\@.
To better
compare KWS with PBE and CTS, we also configure it through examples.
% TODO (resolved) associate is very abstract and tells us
% less about what is going on than the new version

% hope........
% C: explain pure technique vs evaluate-able technique vs comparable
% maybe! we can just replace the hope, or even refer to or logchunks
% experience here / later
From each example, we extract a list of keywords that we hope should
also appear in, or close to, the targeted chunk of new input.
Finally, we merge the lists from all examples to build one unified
list of the most commonly occurring keywords for the search with KWS.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
To fully comprehend how difficult the task of build log analysis really
is without any a priori knowledge, we include a comparison with a
baseline of
picking lines at random from the build log.
RLR mimics the
situation of guessing blindly which lines are interesting.
The only configuration option for RLR is the number of lines it should
retrieve.
For a comparison to the other techniques (whose number of
% M: but wait, this is not really true for KWS, right?
% TODO Moritz: C: sure it is.

% for KWS we vary the number of lines we extract around a found word
returned lines is dynamic), we configure RLR to return the average
number of lines in the chunks of the training examples.

@@

% TODO Caro: I like this explanation of structural categories and
% would leave it here (slightly adapted), but I think
% struct.
%categ.
%should be mentioned earlier -- not sure if you know a
% better place, but how about sec.
%3.1? i don't think people should
% have to read an example section -- which they might skip -- to
% get to know of this important concept!

% C: indeed it's a bit too important to skip
% though can we reasonably explain this without introducing the
% exact techniques first?
% we can also try to start with the example section

@@

CTS will rank the lines from an analyzed build log which are most
similar to the chunks in the training examples
from \Cref{lst:chunk-example}.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
% TODO Caro: How well does it deal with the third example?
% TS has so much magic & this example never ran in our study
% note: I include no notice of how 'good' it runs here
% if we look at the used words: they are very different in both examples

@@

% TODO Moritz: redo figure
% depending on the size of changes / keeping figure uniformity
% we can also do 'pair-animating'
\begin{figure*}[tb]
	\centering
	\includegraphics[width=\textwidth, trim={1.6cm 2.5cm 0.2cm 4.8cm},
  clip]{img/study.pdf}
	\caption{Study design of the technique comparison study.}
	\label{fig:study}
\end{figure*}

In the literature survey, we noted that previous work seemed to choose
a log analysis technique arbitrarily and that is a lack of guidance on
when to use which technique.
% add (see \Cref{sec:lit-sur:discussion}) ?
To address this, in this section, we conduct an empirical study
comparing the three novel chunk retrieval techniques we presented in
\Cref{sec:techniques}.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} How do build log analysis techniques compare?}
% TODO: can we say 'training examples' in 22?
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] With how many training examples does a
	technique perform best?
  \item[\textbf{RQ2.2:}] How structurally variable can training
  examples be?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

For each build log in \emph{LogChunks}, we manually marked
the chunk that describes why the build
failed---the information targeted by most of the works in our
literature survey (see \Cref{sec:lit-sur:discussion}).
To be able to configure the keyword search technique,
we associated each chunk in the data set with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
% TODO Are surrounding markings really the only structural
% category element? I doubt that
% C: ?
If the chunks were, for example, surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

% TODO what does this refer to here? Make it clearer.
%It would refer to the strcutrual categories but
% that is already in the list?
% C: are you talking about the following or the previous paragraph?
% the following one is a more explicit definition of 'example' as
% used in the study

% TODO couldn't it also be chunks? why corresponding?
% C: you took that out already? a (maybe unecessary) specification
% it is always ONE chunk !
As explained in \Cref{sec:crt-characteristics}, examples are the basic
unit by which we configure each technique.
The full build log text,
the chunk, the search keywords, and the assigned
structural category make
up one \emph{example} in \emph{LogChunks}.

@@

% TODO Didn't we above define ``run'' instead of apply?
% Shouldn't we then also use it here?
% C: see discussion further above about run vs apply
% if we adapt the headings (332 and so on) we can use run
% TODO wow, this starts already super confusing
% C: T.T
We run each of the three chunk retrieval techniques
on all of the 80 projects in
\emph{LogChunks} \circlenum{1}.
For each project, we select training sets of size 1, 2, \dots 5
\circlenum{2}.
We vary the training set size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).

@@

\resizebox{\columnwidth}{!}{%
\centering
\begin{tabular}{lllll}
  \toprule
  & & \textbf{PBE} & \textbf{CTS} & \textbf{KWS} \\

	\midrule

	\textbf{RQ2.1} & \textbf{Training Set Size} & 2 & no influence &
	2 \\

  \midrule

	\textbf{RQ2.2} & \textbf{Structural Categories} & 1 & less
	is better
	& \makecell[l]{best 1 \\ multiple okay} \\

	\midrule

  \multirow{6}{*}{\textbf{RQ2.3}} & \textbf{Precision} &
	\makecell[l]{high \\ (if synthesis succeeds)} &
  medium & low \\

	\cmidrule{2-5}

  & \textbf{Recall} & \makecell[l]{high \\ (if synthesis succeeds)} &
  medium & high \\

	\cmidrule{2-5}

  & \makecell[l]{\textbf{Confidence in} \\ \textbf{Output Correctness}}
  & high & low &
  \makecell[l]{low (precision) \\ high (recall)} \\

	\cmidrule{2-5}

  & \textbf{Output Consumer} & program & human & human \\
  \bottomrule
\end{tabular}%
}
\end{table}

@@

\noindent
\textbf{With how many training examples does PBE perform best? (RQ2.1).}
When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
In fact, unless they
were in some sense redundant, adding more training examples even
hindered the applicability of PBE.

\noindent
\textbf{How structurally variable can training examples be? (RQ2.2).}
The study results show that chunk retrieval with PBE gives best
results when the log chunks are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based
programs~\cite{mayer2015user}.
PBE is thus suited to retrieve information
chunks that always have the same defining surrounding or internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to start and
end the same way.

\noindent
\textbf{How accurate are the retrievals of PBE? (RQ2.3).}
If the program synthesis succeeds and applying the regular expression
program yields an output, PBE has high precision and recall.
The technique
clearly identifies a failing synthesis or when the regular expression
finds no match on a build log.
Therefore, if PBE produces
an output, the user can have high confidence that it is the desired
output.
This preciseness makes output from PBE chunk retrieval
well-suited for machine consumption and therefore automatic onward
processing.

\subsubsection{Common Text Similarity (CTS)}

\noindent
\textbf{With how many training examples does CTS perform best? (RQ2.1).}
The number of training examples had no noticeable influence on
precision or recall.
Information retrieval techniques
like text similarity commonly learn on a higher number of examples
than we chose in the study.
Future work should investigate how many
examples yield improvements in the chunk retrieval over a single
training example.

\noindent
\textbf{How structurally variable can training examples be? (RQ2.2).}
CTS yields better results the
fewer structural categories are present in the training and test
examples.

\noindent
\textbf{How accurate are the retrievals of CTS? (RQ2.3).}
CTS has good precision and recall on average, though with a high
variation.
This means that the quality of an output by CTS is hard to
determine, which makes it unsuited for automatic processing and requires
a human to further inspect and interpret the output.
This could include semi-automated procedures such as sending
developers an email with the extracted build failure reason.

\subsubsection{Keyword Search (KWS)}
\noindent
\textbf{With how many training examples does KWS perform best? (RQ2.1).}
Going from one to two training examples, KWS's recall improves
significantly.
However, further enlarging the training set
does not lead to further improvements.

\noindent
\textbf{How structurally variable can training examples be? (RQ2.2).}
KWS has a higher recall than the two other techniques for multiple
structural categories present in the training and test examples.
This
makes KWS a good technique if there is little prior knowledge of how
the targeted log chunk is represented in the build log.
For the
example of extracting the reason the build failed, KWS is best suited
if a build can fail in various steps logged by different build
tools and no
pre-categorization of where the build failed is available.

\noindent
\textbf{How accurate are the retrievals of KWS? (RQ2.3).}
While KWS has the highest recall of all three techniques, its
precision is the lowest.
The output of a chunk retrieval with KWS is
well-suited to be read by humans, but ill-suited for consumption by
automated tools.

@@

The first and most important aspect that influences the decision for a
chunk retrieval technique is the presence of different structural
categories in the log (or lack therefore).
Are the targeted log
chunks always present in the same structural way within the build logs
(first question in \Cref{fig:crt-recommendation})?  If so, the chunks
in all training examples and the analyzed build log are in the same
structural category
%TODO ...
%and what? PBE is the best technique?
% C: this is more a clearer 'introduction' to structural categories
% if we believe this to be explained well enough here we can also
% leave it out

% TODO Caro: check that this does not get a mini paragraph
If the chunks are from multiple structural categories and recall is
more important than precision, we recommend to use KWS\@.
% TODO because ?
% C: looking for reference to tree figure or to results section?

@@

% TODO Caro: fill in the maven analyzer plugin and others.
% C: aha did we evaluate them?...
% C: so I'll add a few more and anecdotally say what each does?
% the list will be in now way complete but maybe give an impression
% as if we are close to what industry says.
\textbf{Limitation to Scholarly Articles.} We limited our literature
survey to scholarly articles.
However, the field of build log analysis is extremely relevant to
practitioners, too.
While it is difficult to systematically sight all such non-scientific
material, we ran several Google search queries related to build log
analysis and evaluated them informally.
Our findings include the Jenkins build log analyzer and a web page
on which Microsoft details how its CI service, Azure Pipes, uses a
PBE-approach for certain log formats such as Python.
This inspired the choice of PBE in \Cref{sec:choice}.
% TODO Caro: end with claim that we are still close to
% industry approaches

@@

Overall, we believe our implementations and their weaknesses stand
prototypical for the techniques.
We tried to limit idiosyncrasies as
much as possible, by choosing standard approaches and minimizing
configuration, instead of parameterizing and fine-tuning methods
specific to our data set.

@@

\textbf{Few Samples with Many Structural Categories.}
Our comparison study includes fewer measurements with many structural
categories than with one structural category category.
50\% of the measurements were conducted with one structural category
in the training and test sets
(34\% with two, 16\% with more than two categories).
% TODO check resolved: Also tell % of what?
This distribution mirrors the
structural categories in a real-world data set, where there were
mostly few structural categories within one project.
In addition, the
third of the measurements we conducted with two structural categories
already showed the negative effect of an increasing number of
structural categories on the performance of the chunk retrieval
techniques.

\section{Future Work}
In this section, we describe what we believe are fruitful future
research directions in the field of build log analysis.
We base our
assessment on the results of the literature survey and combine it with
findings from our technique comparison study.

@@

\textbf{Further Analysis of \emph{LogChunks}.}
We created the
\emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
For example, we can investigate the keywords to answer which
keywords developers use to mark errors that lead to a build failure
within build logs.

@@

We evaluated the performance of these chunk retrieval techniques on the
\emph{LogChunks} data set and saw varying results.
CTS had the highest average F$_{1}$-score with 51\%, while the other
techniques showed higher average scores for precision (95\%, PBE) and
recall (70\%, KWS).
Overall, all techniques vastly outperformed a
baseline of random line retrieval.
